Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-13 paper/paper.tex
k=3 to the appendix

\section{An Optimal Algorithm for $k=3$}

We define the algorithm \TAlg in the following way.
\TAlg maintains the components for each node.
Intially, each node is in its own singleton component.
Upon receiving a request $(u,v)$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, where it each component has all of its nodes in one server.
If no such partition exists, \TAlg resets all its components and finishes the phase.

@@

>>>>

@@

  \section{An Optimal Algorithm for $k=3$ (most likely wrong)}

  We define the algorithm \TAlg in the following way.
  \TAlg maintains components for each node.
  Intially, each node is in its own singleton component.
  Upon receiving a request $(u,v)$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, where it each component has all of its nodes in one server.

  \maciek{Component reseting magic}
  Now we define what \TAlg does when no such partition exists.
  If the resulting component (of $u$ and $v$) has size $4$, then \TAlg resets all internal requests that concern this component.
  Otherwise, \TAlg resets all its components and ends the phase.
